Relative parabolic factorizations of Chevalley groups

### 2015-09-05 stability-conditions.tex
Some references on large stable ranks

Let $R$ be a commutative ring. We denote by $\Max(R)$ its \emph{maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology. For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
The following result gives an upper estimate for the absolute stable rank (see~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
\begin{prop}
Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
$X_1\ldots, X_m$ such that $\dim(X_i)\leqslant d$ for every $i$. Then $\asr(A)\leqslant d+1$.
\end{prop}
%TODO: Add more comments?
From the definition of $\asr(I)$ and the previous proposition it follows that
\[ \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
\begin{rem}
There exist examples of rings for which the first inequality in the above formula is strict. Namely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}. However, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
\end{rem}

>>>>

Let $R$ be a commutative ring. We denote by $\Max(R)$ its \emph{maximum spectrum} i.e. the set of maximal ideals of $R$ equipped with Zariski topology. For a topological space $X$ denote by $\dim(X)$ its usual topological dimension.
The following result gives an upper estimate for the absolute stable rank (see~\cite[Theorem~2.3]{EO}, \cite[Theorem~3.7]{MKV}).
\begin{prop}\label{prop:asr-dimmax}
Let $R$ be a commutative ring whose maximum spectrum $\Max(R)$ can be covered with a finite family of subsets 
$X_1\ldots, X_m$ such that $\dim(X_i)\leqslant d$ for every $i$. Then $\asr(A)\leqslant d+1$.
\end{prop}
%TODO: Add more comments?
From the definition of $\asr(I)$ and the previous proposition it follows that
\[ \sr(I)\leqslant\asr(I)\leqslant\asr(R)\leqslant \dim(\Max(R))+1\leqslant\dim(\Spec(R))+1. \]
\begin{rem}
There exist examples of rings for which the first inequality in the above formula is strict. Namely, there are rings of stable rank $1$ but of absolute stable rank $\geqslant2$, see~\cite{MKV}. However, \cite[Theorem~1.3]{MKV} shows that $\sr(R)=\asr(R)$ for any principal ideal ring $R$.
\end{rem}
\cref{prop:asr-dimmax} shows in particular, that every Dedekind domain $R$ satisfies $\asr(R)\leqslant2$, and that $\sr(A)[x]\leqslant3$ for every locally principal ring $A$. It is shown in \cite{GruMenVasSL2ZxSL2kxy} that $\sr(\mathbb{Z}[x])=3$. Note that $\sr(\mathbb{Z}[x_1,\ldots,x_n])=n+1$ if $n>1$ \cite[Example after Theorem~18.2]{VasSusSerreProblem}.
